An exact Riemann solver for one-dimensional multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state

### 2019-06-13 Manuscript revise 20190612.tex
3

\begin{equation} \label{yield1}
  \left\{
  \begin{aligned}
	& \text{an elastic  rarefaction} & \text{if}  \ \hat{s}_{xxL(R)}<\frac{2}{3}Y^{0},\\
	& \text{a plastic rarefaction} & \text{if} \ {s}_{xxL(R)} = \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y^{0},\\
	& \text{an elastic rarefaction  and a following plastic rarefaction} &  \text{if} \ {s}_{xxL(R)} < \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y^{0},\\
	& \text{an elastic shock} & \text{if}  \ \hat{s}_{xxL(R)}> -\frac{2}{3}Y^{0},\\
	& \text{a plastic shock} & \text{if} \ {s}_{xxL(R)} = -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y^{0},\\
	& \text{a elastic shock and a following plastic shock} &  \text{if} \ {s}_{xxL(R)} > -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y^{0}.
\end{aligned}\right.
\end{equation}

Combining (\ref{shock1}) and (\ref{yield1}), we can find, in any one side of the wave structure of this Riemann problem, there are six cases showed in Table \ref{tab:cases}, where capital letters ''S'' and ''R'' mean the shock and rarefaction wave, respectively; superscript letters ''E'' and  ''P'' indicate the elastic or plastic state of a wave, respectively. Otherwise, the  subscript $L$ or  $R$  are omitted for simplification.

>>>>

\begin{equation} \label{yield1}
  \left\{
  \begin{aligned}
	& \text{an elastic  rarefaction} & \text{if}  \ \hat{s}_{xxL(R)}<\frac{2}{3}Y^{0},\\
	& \text{a plastic rarefaction} & \text{if} \ {s}_{xxL(R)} = \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y_{0},\\
	& \text{an elastic rarefaction  and a following plastic rarefaction} &  \text{if} \ {s}_{xxL(R)} < \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y_{0},\\
	& \text{an elastic shock} & \text{if}  \ \hat{s}_{xxL(R)}> -\frac{2}{3}Y_{0},\\
	& \text{a plastic shock} & \text{if} \ {s}_{xxL(R)} = -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y_{0},\\
	& \text{an elastic shock and a following plastic shock} &  \text{if} \ {s}_{xxL(R)} > -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y_{0}.
\end{aligned}\right.
\end{equation}

Combining (\ref{shock1}) and (\ref{yield1}), we can find, in any side of the wave structure of this Riemann problem, there are six cases showed in Table \ref{tab:cases}, where capital letters ''S'' and ''R'' mean the shock and rarefaction wave, respectively; superscript letters ''E'' and  ''P'' indicate the elastic or plastic state of a wave, respectively. Otherwise, the  subscript $L$ or  $R$  are omitted for simplification.
